### 2016-04-25 ch03-lrm/nonparametric.tex
Noise variance

The local parameters $\theta$  
\begin{equation}
\theta \isdef 
\begin{bmatrix}
\theta_A\\ 
\theta_B\\
\theta_C
\end{bmatrix}
\qquad \text{ with }
\theta_A \isdef
\begin{bmatrix}
a_1\\ \vdots\\ a_{\order{A}}
\end{bmatrix}
\text{, }
\theta_B \isdef
\begin{bmatrix}
b_0\\ \vdots\\ b_{\order{B}}
\end{bmatrix}
\text{, and }
\theta_C \isdef
\begin{bmatrix}
c_0\\ \vdots\\ c_{\order{C}}
\end{bmatrix}
\end{equation}
in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}, we consider a local window
\begin{equation}
  \LocalWindow[k] 
  \isdef
  \Set{
    \omega_{k+r} 
    | 
    r \in \LocalShifts{k}
  }
\end{equation}
with $\LocalShifts{k} \isdef \Set{-\numel{W}, -\numel{W}+1, \ldots, 0, \ldots, \numel{W}}$
such that the local window around $\omega_k$ consists of $\numel{\LocalWindow} = 2 \numel{W} + 1$ bins. 
If one denotes the input/output spectra in such a local frequency window $\LocalWindow[k]$ as
\begin{equation}
  \LocalVector{U}_k \isdef 
  \mat{
    U(\omega_{k-\numel{W}})\\
    \vdots\\
    U(\omega_{k})\\
    \vdots\\
    U(\omega_{k+\numel{W}})\\
  }
  \text{ and }
  \LocalVector{Y}_k \isdef 
  \mat{
    Y(\omega_{k-\numel{W}})\\
    \vdots\\
    Y(\omega_{k})\\
    \vdots\\
    Y(\omega_{k+\numel{W}})\\
  }
  \text{,}
\end{equation}
and similarly for the other quantities, equation \eqref{eq:output-error-FD} limited to $\LocalWindow[k]$ can be written as
\begin{equation}
  \LocalVector{Y}_k  = {\true{\LocalVector{G}}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
\text{,}
\end{equation} 
where $\hadamard$ denotes the element-wise product (also, Hadamard product).
Substituting $\true{\LocalVector{G}}$ and $\LocalVector{T}$ with the local models $\LocalModel{G}$ and $\LocalModel{T}$ and neglecting the influence of $\LocalVector{V}$ yields
\begin{equation}
  \LocalVector{Y} 
  \approx 
  \hat{\LocalVector{Y}} 
    =
      \LocalModel{G} \hadamard \LocalVector{U} + \LocalModel{T}
      \text{.}
      \label{eq:local-system-equations}
\end{equation}
Note that this encompasses $\nWind$ complex equations in the $\nth = \order{A} + \order{B} + \order{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
Consequently, a necessary condition to compute the model parameters is that
\begin{equation}
  \DOF = \nWind - \nth
       = 2 \numel{W} - \order{A} - \order{B} - \order{C} - 1
\end{equation}
is positive.
To effectively compute the local model parameters, the equation error in \eqref{eq:local-system-equations} is minimized by formulating a quadratic cost function:
\begin{equation}
  \LocalVector{\CostFunc{\LRIC}} 
    \isdef 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)^{\HT} 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)
   \label{eq:costfunc:LRIC}
   \text{.}
\end{equation}
Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires starting values and time-consuming iterative optimization schemes to obtain a parameter estimate.
We denote such a method as $\lric{\numel{W},\order{B},\order{A},\order{C}}$.

\subsection{The Local Rational Method}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced in \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
      \label{eq:nparam:LRM:costFunc}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\order{C}}
    }
    \text{.}
\end{align}
In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
\begin{equation}
    \LocalVector{d}^{n} 
    \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$}
\end{equation}
where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.

This formulation facilitates to solve the problem in a one-step approach:
\begin{equation}
  \LocalVector{\theta}_{\LRM} 
    \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
    = \KTK{\LocalMatrix{K}} \LocalVector{Y}
    \label{eq:nparam:LRM:normalEquations}
\end{equation}
where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.

\TODO{hier voortschrijven: ruisvariantie berekenen}

\begin{remark}
This system can only be solved reliably if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution.
This can be obtained e.g. using random phase multisines or random input signals.
\end{remark}

@@

In the simulations, we consider a discrete-time second order system with transfer function
\begin{equation}
\true{G}(z) = \frac{0.64587 z + 0.64143}
                                      {47.9426 z^2 - 51.2955 z + 46.9933}
                                      \text{,}
\end{equation}
this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$.
The system is scaled such that its peak amplitude is $3\unit{dB}$ and the 
As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
The gain of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int\limits_{\BW} \powerspec{\true{Y}}(\omega) \dd\omega}
            {\int\limits_{\BW} \powerspec{V}(\omega) \dd{\omega}}
  % \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
  %           {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\powerspec{\bullet}$ denotes the \gls{PSD} of $\bullet$ and $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to $\set{10, 20, 40, 60, \infty} \unit{dB}$

@@

\begin{figure}
  \centering
  \remakeNextFigure
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system.}
  \label{fig:nparam:mc:singleTuple}
\end{figure}

@@

\TODO{discuss experiment + figure about PRESS}

>>>>

The local parameters $\theta$  
\begin{equation}
\theta \isdef 
\begin{bmatrix}
\theta_A\\ 
\theta_B\\
\theta_C
\end{bmatrix}
\qquad \text{ with }
\theta_A \isdef
\begin{bmatrix}
a_1\\ \vdots\\ a_{\order{A}}
\end{bmatrix}
\text{, }
\theta_B \isdef
\begin{bmatrix}
b_0\\ \vdots\\ b_{\order{B}}
\end{bmatrix}
\text{, and }
\theta_C \isdef
\begin{bmatrix}
c_0\\ \vdots\\ c_{\order{C}}
\end{bmatrix}
\end{equation}
in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}, we consider a local window
\begin{equation}
  \LocalWindow[k] 
  \isdef
  \Set{
    \omega_{k+r} 
    | 
    r \in \LocalShifts{k}
  }
\end{equation}
with $\LocalShifts{k} \isdef \Set{-\numel{W}, -\numel{W}+1, \ldots, 0, \ldots, \numel{W}}$
such that the local window around $\omega_k$ consists of $\numel{\LocalWindow} = 2 \numel{W} + 1$ bins. 
If one denotes the input/output spectra in such a local frequency window $\LocalWindow[k]$ as
\begin{equation}
  \LocalVector{U}_k \isdef 
  \mat{
    U(\omega_{k-\numel{W}})\\
    \vdots\\
    U(\omega_{k})\\
    \vdots\\
    U(\omega_{k+\numel{W}})\\
  }
  \text{ and }
  \LocalVector{Y}_k \isdef 
  \mat{
    Y(\omega_{k-\numel{W}})\\
    \vdots\\
    Y(\omega_{k})\\
    \vdots\\
    Y(\omega_{k+\numel{W}})\\
  }
  \text{,}
\end{equation}
and similarly for the other quantities, equation \eqref{eq:output-error-FD} limited to $\LocalWindow[k]$ can be written as
\begin{equation}
  \LocalVector{Y}_k  = {\true{\LocalVector{G}}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
\text{,}
\end{equation} 
where $\hadamard$ denotes the element-wise product (also, Hadamard product).
Substituting $\true{\LocalVector{G}}$ and $\LocalVector{T}$ with the local models $\LocalModel{G}$ and $\LocalModel{T}$ and neglecting the influence of $\LocalVector{V}$ yields
\begin{equation}
  \LocalVector{Y} 
  \approx 
  \hat{\LocalVector{Y}} 
    =
      \LocalModel{G} \hadamard \LocalVector{U} + \LocalModel{T}
      \text{.}
      \label{eq:local-system-equations}
\end{equation}
Note that this encompasses $\nWind$ complex equations in the $\nth = \order{A} + \order{B} + \order{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
Consequently, a necessary condition to compute the model parameters is that
\begin{equation}
  \DOF = \nWind - \nth
       = 2 \numel{W} - \order{A} - \order{B} - \order{C} - 1
       \label{eq:nparam:DOF}
\end{equation}
is positive.
To effectively compute the local model parameters, the equation error in \eqref{eq:local-system-equations} is minimized by formulating a quadratic cost function:
\begin{equation}
  \LocalVector{\CostFunc{\LRIC}} 
    \isdef 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)^{\HT} 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)
   \label{eq:costfunc:LRIC}
   \text{.}
\end{equation}
Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires starting values and time-consuming iterative optimization schemes to obtain a parameter estimate.
We denote such a method as $\lric{\numel{W},\order{B},\order{A},\order{C}}$.

Note that the estimated \gls{FRF} is given by evaluating the local model $\LocalModel{G}$:
\begin{equation}
  \hat{G}_{\LRIC}(\omega_k) \isdef \LocalModel[k]{G}(d=0)
  \text{.}
\end{equation}

\subsection{The Local Rational Method}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced in \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
      \label{eq:nparam:LRM:costFunc}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
  \label{eq:nparam:linearRegression}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\order{C}}
    }
    \text{.}
\end{align}
In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
\begin{equation}
    \LocalVector{d}^{n} 
    \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$}
\end{equation}
where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.

This formulation facilitates to solve the problem in a one-step approach:
\begin{equation}
  \estimated{\LocalVector{\theta}}_{\LRM} 
    \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
    = \KTK{\LocalMatrix{K}} \LocalVector{Y}
    \label{eq:nparam:LRM:normalEquations}
\end{equation}
where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.
Furthermore, it is possible to define the relationship between the measured output spectrum $\LocalVector{Y}$ and the periodic output spectrum $\estimated{\LocalVector{Y}}$:
\begin{equation}
  \estimated{\LocalVector{Y}} 
  = \LocalMatrix{K} \LocalVector{\theta}_{\LRM} 
  = \LocalMatrix{K} \pinv{\LocalMatrix{K}} \LocalVector{Y}
  = \LocalMatrix{H} \LocalVector{Y}
\end{equation}
where $\LocalMatrix{H}$ is sometimes called the `hat' matrix since it projects measurements ($\LocalVector{Y}$) onto the estimates ($\estimated{\LocalVector{Y}}$).
It should be noted that the hat matrix is idempotent~\citep[Section 2.1.1]{Cook1982}.

Following the approach in \citet[equation (12) and further]{Pintelon2010LPM1} or \citet[Chapter 2]{Cook1982}, the (ordinary) residuals $\LocalVector{E}$ of the fit are given by
\begin{equation}
  \LocalVector{E} = \LocalVector{Y} - \estimated{\LocalVector{Y}}
  = \LocalVector{Y} - \LocalMatrix{H}\LocalVector{Y}
  =  \left( \Identity{\nWind} - \LocalMatrix{H} \right) \LocalVector{Y}
  \text{.}
\end{equation}
Substitution of \eqref{eq:nparam:linearRegression} in this equation yields
\begin{align}
  \LocalVector{E}  
  &= (\I - \LocalMatrix{H})(\LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V})\\
  &= (\I - \LocalMatrix{H}) \LocalVector{V} + (\I - \LocalMatrix{H})\LocalMatrix{K}\LocalVector{\theta}\\
  &= (\I - \LocalMatrix{H}) \LocalVector{V} + \LocalMatrix{K}\LocalVector{\theta} - \LocalMatrix{K} \pinv{\LocalMatrix{K}} \LocalMatrix{K} \LocalVector{\theta}\\
   &= (\I - \LocalMatrix{H}) \LocalVector{V}
\end{align}
since $\LocalMatrix{K} \pinv{\LocalMatrix{K}} \LocalMatrix{K} = \LocalMatrix{K}$ by construction of the pseudo-inverse~\citep{Penrose1955}.
This equation relates the residuals $\LocalVector{E}$ to the noise $\LocalVector{V}$, which aids to estimate the noise variance:
\begin{equation}
  \estimated{\sigma}^2_{\LocalVector{V}} =
    \frac{1}{\DOF} 
     \LocalVector{E}^{\HT} \LocalVector{E}
\end{equation}
as elaborated in~\citep[Appendix B]{Pintelon2010LPM1}.
Note that $\DOF$ indicates the degrees of freedom of the residuals as in \eqref{eq:nparam:DOF} and could also be computed as either the rank or the trace of the idempotent matrix $(\I - \LocalMatrix{H})$.

\begin{remark}
This system can only be solved reliably if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution from the contribution $\LocalModel{G} \LocalModel{U}$.
This can be obtained e.g. using random phase multisines or random input signals.
\end{remark}

@@

In the simulations, we consider a discrete-time second order system with transfer function
\begin{equation}
\true{G}(z) = \frac{0.64587 z + 0.64143}
                                      {47.9426 z^2 - 51.2955 z + 46.9933}
                                      \text{,}
\end{equation}
this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$, $\damping=0.05$.
The system is scaled such that its peak amplitude is $3\unit{dB}$ and hence its $3\unit{dB}$ bandwidth can be read easily from bode plots.
As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
The gain $\kappa$ of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int\limits_{\BW} \powerspec{\true{Y}}(\omega) \dd\omega}
            {\int\limits_{\BW} \powerspec{V}(\omega) \dd{\omega}}
  % \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
  %           {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\powerspec{\bullet}$ denotes the \gls{PSD} of $\bullet$ and $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to \[
\SNR_{\BW} \in \set{10, 20, 40, 60, \infty} \unit{dB}\text{.}
\]

@@

\begin{figure}
  \centering
  \remakeNextFigure
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system which has been highlighted.}
  \label{fig:nparam:mc:singleTuple}
\end{figure}

@@

### 2016-04-25 config/styles.inc.tex
Actually include MC figures
Some discussion on LRM results
Noise variance

% http://tex.stackexchange.com/questions/287975/pgfplots-layer-issue
\pgfplotsset{
/pgfplots/layers/mylayer/.define layer set=
{axis background,axis grid,main,axis ticks,axis lines,axis tick labels,axis descriptions,axis foreground}
{/pgfplots/layers/standard}
}
\pgfplotsset{/dummy/workaround/.style={/pgfplots/axis on top}}

@@

@@

@@

%TODO: replace *res -> *meas
\pgfplotsset{results/.style={solid,line width=0.7pt}}
\pgfplotsset{linmsres/.style={color=linms,results}}
\pgfplotsset{qlogmsres/.style={color=qlogms,results}}
\pgfplotsset{clogmsres/.style={color=clogms,results}}
\pgfplotsset{plogmsres/.style={color=plogms,results}}

@@

>>>>

% http://tex.stackexchange.com/questions/287975/pgfplots-layer-issue
\pgfplotsset{
/pgfplots/layers/mylayer/.define layer set=
{axis background,axis grid,pre main,main,axis ticks,axis lines,axis tick labels,axis descriptions,axis foreground}
{/pgfplots/layers/standard}
}
\pgfplotsset{/dummy/workaround/.style={/pgfplots/axis on top}}

@@

\pgfplotsset{slopegrid/.style={
  mark phase=2,mark repeat=1,samples=2,mark=text,
  color={black!15},forget plot,
  text mark style={}
}}

@@

\colorlet{etfe}{TangoButter3}
\colorlet{lrm7111}{TangoPlum3}
\colorlet{lric7222}{TangoChameleon3}
\colorlet{lrm7222}{TangoSkyBlue3}
\colorlet{lrm6222}{TangoOrange3}
\colorlet{lpm744}{TangoScarletRed3}

@@

% \pgfplotsset{results/.style={solid,line width=0.7pt}}
% \pgfplotsset{linmsres/.style={color=linms,results}}
% \pgfplotsset{qlogmsres/.style={color=qlogms,results}}
% \pgfplotsset{clogmsres/.style={color=clogms,results}}
% \pgfplotsset{plogmsres/.style={color=plogms,results}}

@@

%% MC LRM
\pgfplotsset{mcrmse/.style={dotted}}
\pgfplotsset{mcbias/.style={solid}}
\pgfplotsset{mcvar/.style={dashed}}
